---
title: "Data Summary"
author: "P. Chelle"
format: html
editor: visual
---

```{r, include=FALSE}
library(tidyverse)
model_data <- read.csv("www/model_data.csv")
new_data <- read.csv("www/new_data.csv")
```

## Data Summary

```{r, results='asis', echo=FALSE}
summary_data <- bind_rows(
  model_data |> mutate(Data = "Model"),
  new_data |> mutate(Data = "Model + Collected")
)
summary_data <- summary_data |>
  group_by(Data) |>
  summarise(
    N = n(),
    NCountry = n_distinct(country),
    MedianAge = median(age),
    MinAge = min(age),
    MaxAge = max(age),
    MedianWeight = median(weight),
    MinWeight = min(weight),
    MaxWeight = max(weight)
  )
names(summary_data) <- c(
  "Data", "N", "Unique Countries",
  paste(c("Median", "Min", "Max"), "Age [yrs]"),
  paste(c("Median", "Min", "Max"), "Weight [yrs]")
)
knitr::kable(summary_data)
```

## Weight Data and Model

Points represent the initial data associated with the collected data colored by country.
Lines represent the median, 2.5th and 97.5th percentiles of the model predictions.

```{r, echo=FALSE}
weight_model <- lm(
  log(weight) ~ splines::bs(age, df = 10) + sex,
  data = model_data
)
min_age <- ceiling(min(model_data$age))
max_age <- floor(max(model_data$age))
input_data <- bind_rows(
  data.frame(age = min_age:max_age, sex = "Male"),
  data.frame(age = min_age:max_age, sex = "Female")
)

weight_data <- bind_cols(
  input_data,
  weight = exp(predict(weight_model, newdata = input_data))
) |> mutate(
  weight_min = weight * exp(qnorm(0.975) * sd(weight_model$residuals)),
  weight_max = weight * exp(qnorm(0.025) * sd(weight_model$residuals))
)

ggplot(data = weight_data, aes(x = age, y = weight)) +
  theme_bw() +
  geom_point(data = new_data, mapping = aes(color = country)) +
  geom_line(mapping = aes(y = weight_min), color = "tomato", linewidth = 1) +
  geom_line(mapping = aes(y = weight_max), color = "tomato", linewidth = 1) +
  geom_line(color = "firebrick", linewidth = 1) +
  facet_wrap(~sex) +
  scale_colour_viridis_d() +
  labs(x = "Age [yrs]", y = "Weight [kg]")
```

## Height Data and Model

Points represent the initial data associated with the collected data colored by country.
Lines represent the median, 2.5th and 97.5th percentiles of the model predictions.

```{r, echo=FALSE}
height_model <- lm(
  log(height) ~ splines::bs(age, df = 10) + sex,
  data = model_data
)
height_data <- bind_cols(
  input_data,
  height = exp(predict(height_model, newdata = input_data))
) |> mutate(
  height_min = height * exp(qnorm(0.975) * sd(height_model$residuals)),
  height_max = height * exp(qnorm(0.025) * sd(height_model$residuals))
)

ggplot(data = height_data, aes(x = age, y = height)) +
  theme_bw() +
  geom_point(data = new_data, mapping = aes(color = country)) +
  geom_line(mapping = aes(y = height_min), color = "tomato", linewidth = 1) +
  geom_line(mapping = aes(y = height_max), color = "tomato", linewidth = 1) +
  geom_line(color = "firebrick", linewidth = 1) +
  facet_wrap(~sex) +
  scale_colour_viridis_d() +
  labs(x = "Age [yrs]", y = "Height [cm]")
```
